Verifying Demonstrations

### 2018-11-20 paper/privacy-properties.tex
Removes old stuff we've settled on

%Seb: I have put it in comments to save on space
%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
%location \(l\) against an adversary who is not present in the location.
%Due to the limitations of physical space, two individuals present in the same 
%location will inevitably learn of each other's presence.
%Thus we will only try to prevent individuals who are not present to learn of 
%this presence.}

% \sonja{start of older thoughts}
% Difference to e-voting:
% physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
% \begin{enumerate*}
% \item they participate in the protocol,
% \item they use the protest identifier (cause) for which the count is done,
% \item they meet the eligibility criteria, and
% \item they receive enough proof shares,
% \item that are uploaded to the ledger.
% \end{enumerate*}
% Thus one could participate in a protest and be counted even when physically 
% present at a counter-protest if the two protests are co-located and the 
% participant chooses the corresponding cause/identifier of the original protest.

% Given that all conditions for being counted in a protest are met, individual 
% verifiability implies a receipt \daniel{no, I know my proof is included in 
%  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
%  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
%  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
%  hence receipt-freeness} because being counted implies support for a cause. 
% This also means that besides physical force, coercion can happen by forcing the 
% participate to show a receipt. \daniel{The only receipt we have is the private 
%  key of the protester, with that key the adversary can compute \(\pid = 
%    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
% We thus have to decide between individual verifiability and the privacy 
% properties for e-voting or define privacy properties suitable for the scenario. 
% The ultimate privacy requirement is thus stronger here: in contrast to voting, 
% where it is the content of the vote itself that needs to be unlinkable to the 
% voter, here the fact of having cast a vote at all needs to be unlinkable.

% The privacy properties we need in this context are the following:
% \begin{description}
%  \item[Involuntary participant unlinkability:] \daniel{the name has a 
%      double-negative ring to me} unless the participant discloses the receipt 
%    (by revealing her identity), there is no link between the protest data on 
%    the ledger and the identity of the participant.

%  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
%      too of course} unless the witness discloses the receipt (by revealing her 
%    identity), there is no link between the protest data on the ledger and the 
%    identity of the witness.
% \end{description}

% In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
% As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
% Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
% Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Finally, any temporary identifiers such as pseudonyms should only be reused 
when strictly necessary for the fulfillment of verifiability properties listed 
in \cref{verifiability-properties} to prevent inference on long-term identities 
by repeated samples and side information.

>>>>

Finally, any temporary identifiers, such as pseudonyms, should only be reused 
when strictly necessary for the fulfillment of verifiability properties (in 
\cref{verifiability-properties}) to prevent inference on long-term identities 
by repeated samples and side information.
